% LaTeX file for resume

\documentclass[line,overlapped]{res}
%\addtolength{\hoffset}{-1in}
%\hoffset=-1in
\textwidth=6.6in 
\resumewidth=7.0in 
%\sectionwidth=5.0in
\sectionskip=0.1in
\usepackage{helvetica} 

\setlength{\oddsidemargin}{-.25in}
\setlength{\evensidemargin}{-.25in}


\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\begin{document}

\name{Jonathan A. Bethune}

\address{therenegadeoffunk@gmail.com \hspace{1.63in} Setagaya-ku, Tokyo, Japan}
\address{(070) 4069-4357}
\newsectionwidth{.2in}
\begin{resume}
\section{Introduction}
	I am an experienced software developer and data engineer from New York City. \\
    I have a decade of experience in variety of systems engineering and application development.\\ 
    My dream is to build software that makes the world a better place.

\section{Education}
{\sl Bachelor of Science,} English Education, New York University \hfill 2006\\
{\sl Electrical Engineering and Computer Science,} Engineering, Massachusetts Institute of Technology \hfill no degree
{\sl Master of Information Systems,} University of Phoenix\hfill 2014

\section{Work History}
    {\bf Software Developer,} Knewton, New York City \hfill April 2010 - September 2014
\begin{itemize} \itemsep -2pt
        \item Wrote application code for Java microservices.
        \item Created infrastructure deployment and monitoring tools in Python.
        \item Served for a year as QA Engineer and wrote integration test service.
\end{itemize}
    \vspace{-10pt}
    {\bf Lead Systems Engineer,} Timehop, New York City \hfill November 2014 - August 2015
\begin{itemize} \itemsep -2pt
        \item Managed AWS infrastructure including RDS, EC2, and DynamoDB services.
        \item Served as Site Reliability Engineer responding to alerts and preventing outages.
        \item Created various infrastructure tools using Go and Chef.
\end{itemize} \itemsep -2pt
    \vspace{-10pt}
    {\bf Senior Devops Engineer,} Cloudpassage, San Francisco \hfill August 2015 - Present
\begin{itemize} \itemsep -2pt
        \item Optimized multiple Cassandra clusters and created tools for big data analysis.
        \item Improved scalability and helped reduced AWS costs via data model auditing and automation.
        \item Automated numerous maintenance and deployment tasks using BASH and Chef.
\end{itemize}

\section{Independent / Open Source Projects / Volunteer Work}
{\bf Remote CS Teaching for Kentucky High School} \hfill Fall 2013 - Summer 2014 (Volunteer)

\section{Technical Skills}
   \begin{tabular}{l p{4in}}
       {\sl Languages:}& Python, BASH, Java, C, C++, Ruby, Scala, Go, Haskell\\
       {\sl Data Science:}& Octave, R, Spark, Machine Learning, ELT, Storm\\
       {\sl Ops:}& Unix, AWS, Cassandra, PostgreSQL, MySQL, Chef, Redis, Docker\\
 \end{tabular}

\section{Other Skills}
   \begin{tabular}{l p{4in}}
       {\sl Foreign Languages:}Japanese, Mandarin, Spanish (basic)\\
       {\sl Editing: Copy Editing, Technical Writing, Teaching}
   \end{tabular}

\section{Links}
    \begin{tabular}{l p{4in}}
        {\sl Linkedin: https://www.linkedin.com/in/jonathan-bethune-27ba3331\\
        {\sl Github: https://github.com/therenegadeoffunk\\
    \end{tabular}

\end{resume}
\footnotetext[2]{Source code available at http://github.com/TheRenegadeofFunk/}
\end{document}
